Automated detection of data fabrication using statistical tools

### 2018-04-11 submission/redraft.rmd
Add paragraph

>>>>

### Data collection

We downloaded thirty-six genuine data sets from the publicly available Many Labs (ML) project [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178]. 
The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously. 
Considering the size of the ML project, the transparency of research results, and minimal individual gain for fabricating data, we assumed these data to be genuine. 
For each of the thirty-six locations we computed three summary statistics (i.e., sample sizes, means, and standard deviations) for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations. 
We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
